Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-10 papers/marlowe2019/paper-long.tex
add long version of 2019 paper

Marlowe\footnote{The complete Marlowe project, including semantics and implementation, is available at \url{https://github.com/input-output-hk/marlowe}.} is a domain-specific language (DSL) for implementing financial contracts on blockchain: our initial target is Cardano, but it could be implemented on many DLT platforms, including Ethereum. Marlowe is embedded in Haskell, allowing users selectively to use aspects of Haskell -- typically definitions of constants and simple functions -- to express contracts more readably and succinctly. Section \ref{sec:overview} gives an overview of the language, and the changes made to it since it was originally introduced in ~\cite{isola-marlowe}.

Marlowe is specified by a reference semantics for the language written in Haskell, and we can use that in a number of ways. We can interpret Marlowe contracts in Haskell itself, but we can also use that implementation, compiled into Plutus~\cite{PlutusPlatform}, to interpret Marlowe directly on the Cardano blockchain, see Section \ref{sec:implementation}. We can also execute the semantics -- translated into PureScript -- directly in a browser, to give an interactive simulation environment, see Section \ref{sec:playground}.

>>>>

Marlowe\footnote{The complete Marlowe project, including semantics and implementation, is available at \url{https://github.com/input-output-hk/marlowe}.} is a domain-specific language (DSL) for implementing financial contracts on blockchain: our initial target is Cardano, but it could be implemented on many distributed ledgers (DLT platforms), including Ethereum. Marlowe is embedded in Haskell, allowing users selectively to use aspects of Haskell -- typically definitions of constants and simple functions -- to express contracts more readably and succinctly. Section \ref{sec:overview} gives an overview of the language, and the changes made to it since it was originally introduced in ~\cite{isola-marlowe}.

Marlowe is specified by a reference semantics for the language written in Haskell, and we can use that in a number of ways. We can interpret Marlowe contracts in Haskell itself, but we can also use that implementation, compiled into Plutus~\cite{PlutusPlatform}, to interpret Marlowe directly on the Cardano blockchain, see Section \ref{sec:implementation}. We can also execute the semantics -- translated into PureScript -- directly in a browser, to give an interactive simulation environment, see Section~\ref{sec:playground}.
